---
title: "ReproHack NL, 2019"
output:
    html_document:
        theme: flatly
        css: reprohack.css
params: 
  title: "Leiden University"
  room_location: "Leiden University Library"
  address: "Witte Single Leiden, NL"
  date: "30 November 2019"
  time: "10 am - 4pm"
  bannerurl: "https://github.com/reprohack/reprohack-hq/raw/master/assets/reprohack-banner.png"
  latitude: 53.38119
  longitude: -1.48036
  registration_url: null
  hackpad_url: https://hackmd.io/link-to-copy-of-hackpad/edit
  submission_url: https://link-to-submissionform
  reprohack_repo_url: https://github.com/your_account/reprohack-location-ISOdate
  submission_form_title: ReproHack Paper Submission Form - your event
runtime: shiny
---

![](`r params$bannerurl`)

# **ReproHack @ `r params$title`**
## _A hands-on Reproducibility Hackathon_

<br>

#### **`r shiny::icon("clock")` `r params$time`**
#### **`r shiny::icon("calendar")` `r params$date`**
#### **`r shiny::icon("map-marker-alt")` `r params$room_location`**
#### **`r shiny::icon("map-marked-alt")` `r params$address`**
  

```{r, echo = F, results='asis'}
if(!is.null(params$registration_url)){
  cat(paste0("### [**REGISTER**](", params$registration_url, ")"))
}
```

[![Gitter](https://badges.gitter.im/reprohack/community.svg)](https://gitter.im/reprohack/community?utm_source=badge&utm_medium=badge&utm_campaign=pr-badge)

##### [workshop repository](`r params$reprohack_repo_url`): containing details for participants


***

## **Ways to participate**


<br>

### `r shiny::icon("newspaper")`  **Propose a paper**

##### You've put a lot of effort into making your work reproducible. Now let people learn from and engage with it! 

Benefits to authors:

- **Feedback** on the reproducibility of your work.

- **Appreciation** for your efforts in making your work reproducible.

- Opportunity to **engage others with your research**.

<br>

***

# **PROPOSE**
### **Nominate a paper for Reproduction:**

We invite nominations for papers that have both associated **code** and **data** publicly available. We also encourage analyses based on open source tools as we cannot guarantee participants will have access to specialised licenced software.


```{r, echo=FALSE}
library("shiny")
 wellPanel(a("Nominate Paper", class = "btn btn-primary btn-md",
          href = params$submission_url))
```


## **Proposed papers:**

<br>

```{r, echo=FALSE, message=FALSE, warning=FALSE, eval=require('googlesheets')}
library(googlesheets)
```

```{r, echo=FALSE}
print_contact_links <- function(responses, i){
  row <- responses[i, ]
  twitter <- if(!is.na(row[,"Twitter handle (optional)"])){
  twitter_url <- paste0("https://twitter.com/", gsub(" *@ *", "", row[,"Twitter handle (optional)"]))
  paste0("[<i class='fa fa-twitter'/>](", twitter_url,")")}else{NULL}
  
  github <- if(!is.na(row[,"GitHub username (optional)"])){
  github_url <- paste0("https://github.com/", gsub(" *@ *", "", row[,"GitHub username (optional)"]))
  paste0("[<i class='fa fa-github'/>](", github_url,")")}else{NULL}

  feedback <- if(row[, "Would you like to receive a copy of any feedback on the paper?"] == "Yes"){
    "<i class='fa fa-comment-dots'/>"}else{NULL}
  public <- if(row[,"Can feedback on your paper be made public?"] == "Yes"){
    "<i class='fa fa-globe'/>"}else{NULL}
  
  return(paste(twitter, github, feedback, public))
}
```


```{r, message=FALSE, results='asis', warning=FALSE,  echo=FALSE}
responses_gs <- gs_title(paste(params$submission_form_title, "(Responses)"))
responses <- gs_read(responses_gs)

if(nrow(responses) > 0){

for(i in 1:nrow(responses)){
    cat('\n')     
    cat('\n')
    cat('\n')
    cat("### **", i,". ", as.character(responses[i, "Paper title"]), "**", "\n", "\n", sep = "")
    cat("**", gsub("\n", "", gsub("[*]", "", as.character(responses[i, "Paper citation"]))), "\n**", "\n", "\n", sep = "")
    cat("##### *submitted by ", as.character(responses[i, "Name"]),  print_contact_links(responses, i), "*", "\n")
    cat('\n')
    cat('\n')
    cat("**Why should we attempt to reproduce this paper?**", "\n", "\n")
    cat(as.character(responses[i, "Why should we attempt to reproduce this paper?"]), "\n")
    cat('\n')
    cat("**Paper URL:** [", as.character(responses[i, "Paper URL"]),"](",as.character(responses[i, "Paper URL"]) ,")", "\n")
    cat('\n')
    cat("**Data URL:**", as.character(responses[i, "Data URL"]), "\n")
    cat('\n')
    cat("**Code URL:**", as.character(responses[i, "Code URL"]), "\n")
    cat('\n', "\n")
    cat("**Useful programming skills:**", as.character(responses[i, "Useful programming skills"]), "\n")
    cat('\n', "\n",'\n')
}

}
```



```{r, echo=FALSE}
 wellPanel(a("Refresh proposal list", class = "btn btn-primary btn-md",
          href = "javascript:history.go(0)"))
```



***










